Bayesian Sparsification of $\cplx$-valued networks

### 2020-01-31 paper/paper.tex
comment on the error messages
notes on replications and train splits

In this section we study the complex variational dropout techniques discussed above
on the tasks and datasets, that were studied in prior research on complex-valued networks.
All experiments share the following settings unless specified otherwise:
\begin{itemize}
  \item ADAM optimizer with the base learning rate of $10^{-3}$
  \item learning rate the annealing schedule from \citep{trabelsi_deep_2017}
  \item global gradient clipping within an $\ell_2$-norm ball of radius $0.05$
\end{itemize}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}
    \centering
    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/log-alpha__histograms.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}
    \centering
    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/proba_of_nonzero.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
    tolerance of its mean.
  }
  \label{fig:log-relevance}
\end{figure}

@@

>>>>

In this section we study the complex variational dropout techniques discussed above
on the tasks and datasets, that were studied in prior research on complex-valued networks.
All experiments share the following settings unless specified otherwise:
\begin{itemize}
  \item ADAM optimizer with the base learning rate of $10^{-3}$
  \item learning rate the annealing schedule from \citep{trabelsi_deep_2017}
  \item global gradient clipping within an $\ell_2$-norm ball of radius $0.05$
\end{itemize}
Every experiment is replicated several times to take random effects into account, e.g.
random network initialization prior to ``dense'' stage, randomly ordered batches during
SGD. Throughout every experiment on MNIST-like datasets (sec.~\ref{sub:mnist_like_datasets},
we \textit{fixed} a random subset of the train split of each dataset, and used the test
split to gauge the final performance. Same appriach was applied to CIFAR10 (sec.~%
\ref{sub:cifar10_100} experiments, which could partly expalin the overall poor test
perfomrnace we got from the tested VGG16 model ($\real$ and $\cplx$ version).

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/log-alpha__histograms.pdf}
    % \caption{} \label{fig:log-relevance-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/proba_of_nonzero.pdf}
    % \caption{} \label{fig:log-relevance-proba}
  \end{subfigure}
  \caption{%
    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
    tolerance of its mean.
  }
  \label{fig:log-relevance}
\end{figure}

@@

The set up of the experiment is thus:
Each full three-stage run is replicated five times take random effects into account, e.g.
random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
the sample during SGD.
